% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Sang woo Ham}

\basicInfo{
  \email{ecosang@gmail.com} 
  \phone{+1-765-409-4164} 
  \linkedin[ecosang]{https://www.linkedin.com/in/ecosang}
  \github[ecosang]{https://github.com/ecosang}
  \homepage[website]{https://ecosang.github.io/blog}
}

\section{Education}
\datedsubsection{\textbf{Purdue University}}{West Lafayette, IN} 
\role{Ph.D. in Civil Engineering; Advisor: Prof. Panagiota Karava; GPA: 3.85/4.0} {\hfill Aug. 2016 - Present}
\begin{itemize}
\item{\textbf{Related Courses}: Bayesian Data Analysis, Big Data Analytics, Uncertainty quantification}
\end{itemize}
\datedsubsection{\textbf{Hanyang University}}{Seoul, South Korea} 
\role{M.S. in Architectural Engineering; Advisor: Prof. Jae-weon Jeong; GPA: 4.0/4.0} {\hfill Mar. 2014 - Feb. 2016}
\begin{itemize}
\item{\textbf{Related Courses}: Building Automation and Control System, Data Mining, Computational Fluid Mechanics}
\end{itemize}
\datedsubsection{\textbf{Hanyang University}}{Seoul, South Korea} 
\role{B.S. in Civil Engineering; GPA: 3.83/4.0 (SUMMA CUMLAUDE, 2nd rank out of 72)} {\hfill Mar. 2007 - Feb. 2014}
\begin{itemize}
\item{\textbf{Related Courses}: Heat Transfer, HVAC System Design}
\end{itemize}

\section{Research Experience}
\datedsubsection{\textbf{Sociotechnical Systems to Enable Smart and Connected Energy-Aware Residential Communities (NSF No.1737591)}}{Herrick Lab., Purdue Univ., West Lafayette, IN} 
\role{Graduate Research Assistant} {\hfill   Aug. 2016 - Present}
\begin{itemize}
\item{Major assistant to write the proposal including literature review, illustration, and idea development}
\item{Installation, and prototyping of WiFi-based smart home devices (Smart thermostat, Power meter, Tablet, Speaker)}
\item{Design, documentation, and of smart home database and application with software engineers}
\item{Development of Bayesian-based online heating and cooling energy prediction/energy normalization model for eco-feedback via visual/voice user-interactive devices}
\item{Project management with multiple students, faculties, and field engineers}
\end{itemize}
\datedsubsection{\textbf{Development of liquid desiccant and evaporative cooling assisted 100\% outdoor air system (NRF of Korea, No.2012001927)}}{BMES Lab., Hanyang Univ., Seoul, Korea} 
\role{Graduate Research Assistant} {\hfill   Mar. 2014 - Feb. 2016}
\begin{itemize}
\item{Design and installation of heat exchanger test chamber}
\item{Develop numerical simulations and experiment of indirect evaporative cooler}
\item{Develop control simulations of liquid-desiccant and dew point cooling based 100\% outdoor air system on BCVTB}
\item{Develop simplified model of PEM fuel cell based on experiment}
\end{itemize}
\datedsubsection{\textbf{Development of energy efficient modular data center for PUE below 1.5 (KITECH, No. 10045236)}}{BMES Lab., Hanyang Univ., Seoul, Korea} 
\role{Undergraduate Research Assistant} {\hfill   Mar. 2013 - Feb. 2014}
\begin{itemize}
\item{Develop Energy simulation of various economizers in a modular data center}
\item{Develop CFD simulations and experiments on a modular data center}
\end{itemize}

\section{Publications}
\datedsubsection{\textbf{Journal Papers}}{} 
\begin{itemize}\setlength\itemsep{0.5em}\setlength\itemindent{-.1in}
\item{\textbf{Ham, S.-W.}, and Karava, P. (2021). A Scalable Building Modeling Approach using Probabilistic Deep learning. In-preparation.}
\item{\textbf{Ham, S.-W.}, Karava, P., Bilionis, I., and Braun, J. (2020). A data-driven building energy normalization model for eco-feedback design in smart and connected multi-family residential buildings. Submitted to Journal of Building Performance Simulation.}
\item{\textbf{Ham, S.-W.}, Karava, P., Bilionis, I., and Braun, J. (2020). Online model for unit-level heating and cooling energy use prediction in multi-family residential buildings for eco-feedback design. Submitted to Applied Energy.}
\item{Kim, H.-J., \textbf{Ham, S.-W.}, Yoon, D.-S., and Jeong, J.-W. (2017). Cooling performance measurement of two cross-flow indirect evaporative coolers in general and regenerative operation modes. \textit{Applied Energy},  Vol.195, pp.268-277. \href{https://doi.org/10.1016/j.apenergy.2017.03.053}{doi}}
\item{\textbf{Ham, S.-W.}, and Jeong, J.-W. (2016). Dew point evaporative heat exchanger (DPHX): Design and performance analysis. \textit{Energy}, Vol.101, pp.132-145. \href{https://doi.org/10.1016/j.energy.2016.02.019}{doi}}
\item{\textbf{Ham, S.-W.}, Lee, S.-J., and Jeong, J.-W. (2016). Operating energy savings in a liquid desiccant and dew point evaporative cooling-assisted 100\% outdoor air system. \textit{Energy and Buildings}, Vol.116, pp.535-552. \href{https://doi.org/10.1016/j.enbuild.2016.02.011}{doi}}
\item{\textbf{Ham, S.-W.}, Jo, S.-Y., Dong, H.-W., and Jeong, J.-W. (2015). A simplified PEM fuel cell model for building cogeneration applications. \textit{Energy and Buildings}, Vol 107, pp.213-225. \href{https://doi.org/10.1016/j.energy.2016.02.019}{doi}}
\item{Kim, M.-H., Park, J.-Y., \textbf{Ham, S.-W.}, and Jeong, J.-W. (2015). Energy conservation benefit of water-side free cooling in a liquid desiccant and evaporative cooling-assisted 100\% outdoor air system. \textit{Energy and Buildings},  Vol.104, pp.302-315. \href{https://doi.org/10.1016/j.enbuild.2015.07.029}{doi}}
\item{\textbf{Ham, S.-W.}, and Jeong, J.-W. (2015). Impact of aisle containment on energy performance in a data center with integrated water-side economizer. \textit{Applied Thermal Engineering}, Vol.105, pp.372-384.  \href{https://doi.org/10.1016/j.applthermaleng.2015.05.069}{doi}}
\item{\textbf{Ham, S.-W.}, Park, J.-S., and Jeong, J.-W. (2015). Optimum supply air temperature ranges of various air-side economizers in a modular data center. \textit{Applied Thermal Engineering}, Vol.77, pp.163-179. \href{https://doi.org/10.1016/j.applthermaleng.2014.12.021}{doi}}
\item{\textbf{Ham, S.-W.}, Kim, M.-H., Choi, B.-N., and Jeong, J.-W. (2015). Simplified server model to simulate data center cooling energy consumption. \textit{Energy and Buildings}, Vol.86, pp.328-339. \href{http://dx.doi.org/10.1016/j.enbuild.2014.10.058}{doi}}
\item{\textbf{Ham, S.-W.}, Kim, M.-H., Choi, B.-N., and Jeong, J.-W. (2015). Energy saving potential of various air-side economizers in a Modular Data Center. \textit{Applied Energy}, Vol.138, pp.258-275. \href{http://dx.doi.org/10.1016/j.apenergy.2014.10.066}{doi}}
\item{Kim, M.-H., \textbf{Ham, S.-W.}, Park, J.-S., and Jeong, J.-W. (2014). Impact of integrated hot water cooling and desiccant-assisted evaporative cooling system on energy savings in a data center. \textit{Energy}, Vol.78, pp.384-396. \href{http://dx.doi.org/10.1016/j.energy.2014.10.023}{doi}}
\end{itemize}
\datedsubsection{\textbf{Conference Proceedings}}{} 
\begin{itemize}\setlength\itemsep{0.5em}\setlength\itemindent{-.1in}
\item{\textbf{Ham, S.}, and Karava, P. (2019). Online Building Energy Model to Evaluate Heating and Cooling-related Behavior Changes for Eco-feedback in a Multifamily Residential Building. \textit{Proceedings of the 16th IBPSA Building Simulation Conference}, Rome, Italy, Sept. 2-4, 2019, Page 2379-2387. \href{http://www.ibpsa.org/proceedings/BS2019/BS2019_211234.pdf}{doi}}
\item{\textbf{Ham, S.}, and Karava, P. (2018). Identifying Peer Groups in a Multifamily Residential Building for Eco-Feedback Design. \textit{International High Performance Buildings Conference}, Paper 319. \href{https://docs.lib.purdue.edu/ihpbc/319}{doi}}
\item{\textbf{Ham, S.-W.}, Kim, H.-J., Cho, S.-H., and Jeong, J.-W. (2016). A Variable Volume and Temperature (VVT) Control Strategy for a Liquid-Desiccant and Dew Point Evaporative Cooler-Assisted 100\% Outdoor Air System (LDEOS). \textit{2016 ASHRAE Annual Conference}, St. Louis, MO, June. 25-29, 2016. \href{https://www.techstreet.com/standards/st-16-c048-a-variable-volume-and-temperature-vvt-control-strategy-for-a-liquid-desiccant-and-dew-point-evaporative-cooler-assisted-100-outdoor-air-system-ldeos?product_id=1919925}{doi}}
\end{itemize}
\datedsubsection{\textbf{Presentations}}{} 
\begin{itemize}\setlength\itemsep{0.5em}\setlength\itemindent{-.1in}
\item{Hobbs, G., Watts, R., \textbf{Ham, S.}, and Sipe, J. (2018). Smart and Connected Energy-Aware Residential Communities. \textit{Indiana Housing conference}, September 2018. }
\end{itemize}

\section{Skills}
\begin{itemize}
\item \textbf{Programming Language}: {R, Python, Matlab, SQL, PLC, git}
\item \textbf{Computating Library}: {Pyro, Pytorch, Stan, Tidyverse}
\item \textbf{Software}: {Energyplus, Openstudio, BCVTB, ANSYS Fluent, TRNSYS}
\end{itemize}

\section{Experience}
\datedsubsection{\textbf{R book translation}}{West Lafayette, IN} 
\role{Translator} {\hfill   May. 2018 - Aug. 2018}
\begin{itemize}
\item{Translation of Ch. 2 and 5 of \textbf{Efficient R programming} as a member of R Korea user group community}
\end{itemize}

\section{Scholarsip, Awards, Certifications}
\datedsubsection{\textbf{Scholarship}}{} 
\begin{itemize}
\item{Ross Fellow Scholarship, Purdue Univ., 2016 - 2019}
\item{Top scholarship, Hanyang Univ. 2013 - 2014}
\end{itemize}
\datedsubsection{\textbf{Awards}}{} 
\begin{itemize}
\item{Excellent Paper Award, Conference proceedings of Architectural Institute of Korea, 2014/2016}
\item{Excellence Award, 1st conference of undergraduate mock policy proposal on National Science and Technology Council, 2012}
\end{itemize}
\datedsubsection{\textbf{Certifications}}{} 
\begin{itemize}
\item{Engineer Building Facilities, National Technical Qualification Certificate, 2013}
\item{LEED AP O&M, USGBC, 2012}
\end{itemize}

\end{document}
